When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-02-21 presentation/inbreeding.Rmd
Progress on the fancier bit

## Introduction

>>>>

## Inbreeding depression

```{r lmSim, fig.show='animate', echo = FALSE}
inputPanel(
  sliderInput("Imm", label = "Immigrants", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("ID", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("cost", label = "Strategy Cost", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("mu", label = "Mutation Rate", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  actionButton("mate", "New Generation"),
  actionButton("reset", "Reset")
)

ts    <- reactiveValues();
ts$df <- data.frame(gen = numeric(0), val = numeric(0));

Ds    <- observeEvent(input$mate, {
        new   <- isolate(c(dim(ts$df)[1] + 1, runif(1, 0, 1)));
        isolate(ts$df <- rbind(ts$df, new));
})

rs    <- observeEvent(input$reset, {
       ts$df <- data.frame(gen = numeric(0), val = numeric(0)); 
})

renderPlot({
  par(bg = 'transparent');
  last <- dim(ts$df)[1];
  if(last < 6){
      plot(x = 0:10, y = 0:10, type = "n", ylim = c(0, 1), cex.axis = 1.5,
           cex.lab = 1.5, xlab = "Generation", ylab = "k", bg = "transparent");
      points(x = ts$df[,1], y = ts$df[,2], pch = 20, cex = 1.5, type = "b",
             lwd = 2);
  }else{
      x0 <- last - 5;
      x1 <- last + 5;
      plot(x = x0:x1, y = x0:x1, type = "n", ylim = c(0, 1), cex.axis = 1.5,
           cex.lab = 1.5, xlab = "Generation", ylab = "k");
      points(x = ts$df[x0:x1,1], y = ts$df[x0:x1,2], pch = 20, cex = 1.5, type = "b",
             lwd = 2);
  }
})
```

## Inbreeding tolerance

## Inbreeding avoidance

## Inbreeding preference

## Parker's model
